Opportunities for improvement in the care of adult trauma patients arriving in shock

### 2024-11-29 thesis.Rmd
gjort step analys, fast kortade ner det hela i 2 steg, även noterat fel i reg mellan study.sample och reg.sample

-->
```
## Key results
We found that the most common type of OFI is Clinical judgement error across almost all shock severities and that there are minor if any association between shock severity and OFI.

>>>>

-->
```
## Key results
We found that the most common type of OFI is clinical judgement error across almost all shock severities and there is only statistical significant association between severe shock with a BE of < -10 and OFI.
